### 2014-11-10 SP_simul.Rmd
Finsh the spatial pattern results and figures

#
# Plots of Dq with uniform/Logseries SAD and 10 repetitions!
#
unique(DqT$SAD)

g <- plotDq_Side_Sp(DqT,256,64,"B")
g
setwd("..")
ggsave("Dq_UniLog64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,256,0,"B")
g
ggsave("Dq_UniLog_NumSp_256.png", width=8,height=6,units="in",dpi=600)

#g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
#g

g <- plotDq_Side_Sp(DqT,256,0,"Uniform")
g
ggsave("Dq_Unif_NumSp_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,512,0,"Uniform")
g
ggsave("Dq_Unif_NumSp_512.png", width=8,height=6,units="in",dpi=600)

@@

g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
g

@@

Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))

rm(Dq1,Sad1,pow)

@@

@@

```{r plots_logser_spDq, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

# Plot of the uniform and randomized spatial pattern for a logseries SAD with 64 species and side=256
#

#g <- plotSAD_SpatPat(64,256,"L")
#g 
#setwd("..")
#ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)

#unique(DqT$SAD)

#g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
#g
#ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)

@@

>>>>

#
# Plots of Dq with uniform/Logseries SAD and 10 repetitions!
#
setwd("..")

g <- plotDq_Side_Sp(DqT,256,0,"B")
g
ggsave("Dq_UniLog_NumSp_256.png", width=8,height=8,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,512,0,"B")
g
ggsave("Dq_UniLog_NumSp_512.png", width=8,height=8,units="in",dpi=600)

@@

@@

@@

setwd("Simul")
zq <- readDq_fit(256,8,"Uniform")
g <- plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Unif_8_256.png", width=8,height=6,units="in",dpi=600)

setwd("Simul")
zq <- readDq_fit(256,256,"Uniform")
g <- plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Unif_256_256.png", width=8,height=6,units="in",dpi=600)

@@

```{r plots_logser_spDq, eval=T,echo=F,message=F,warning=F}

@@

## Generate Tables with R2 proportions

```{r R2tbl_Dq, eval=F,echo=F,message=F,warning=F}

Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
  group_by(DqType,SAD,SpatialPattern,NumSp,Side) %>% 
  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))

rm(Dq1,Sad1,pow)
```
